Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-09-20 scagnostics.Rmd
No significant changes.

## Data description
The model describes a neutron star merger and contains 6 free parameters, i.e. each neutron star is described by its mass and radius, and a so-called tidal deformability parameter $\Lambda$. A posterior sample containing 2538 points is available @ligoData and can be used to constrain the parameters. Here we use the "Parametrized-EoS\_nomaxmass\_posterior\_samples.dat" dataset. For details about the modelling and statistical procedure see @Abbott2018exr. A common representation of posterior samples used for interpretatin are so-called "corner plots", i.e. density displays for all 2-d parameter combinations as well as the 1-d profile, highlighting empirically evaluated regions of highest posterior density, which correspond to credibility regions at a given level.
Use Rorys script to make nice version of his corner plot.
Here we generate such a corner plot using the python package "ChainConsumer", highlighting the x and y % CIs. We point out the following features seen from Fig. XX: the combination of the two mass paremters is well constrained (a consequence of how a particular combination, the "chirp mass" enters predictions), other parameters also show patterns of dependence, they are however less pronounces. We highlight the non-linear relation between the radius $R_1$ and $\Lambda$ parameter and the two-pronged structure of the radius $R_1$.
For further study we therefore remove m2 from the dataset. We first look at the distribution in a grand tour display, where we use a scatter plot display combined with alpha blending to study the density distribution in the 5-d parameter space. The grand tour indicates that the data points are found on a curved surface in the five dimensional space. This may stem from a non-linear relation between the parameters, which we will try to uncover using the above developped formalism for new guided tour index functions.

>>>>

## Data description
The model describes a neutron star merger and contains 6 free parameters, i.e. each neutron star is described by its mass and radius, and a so-called tidal deformability parameter $\Lambda$. A posterior sample containing 2538 points is available @ligoData and can be used to constrain the parameters. Here we use the "Parametrized-EoS\_nomaxmass\_posterior\_samples.dat" dataset. For details about the modelling and statistical procedure see @Abbott2018exr. A common representation of posterior samples used for interpretatin are so-called "corner plots", i.e. density displays for all 2-d parameter combinations as well as the 1-d profile, highlighting empirically evaluated regions of highest posterior density, which correspond to credibility regions at a given level.
Use Rorys script to make nice version of his corner plot.
Here we generate such a corner plot using the python package "ChainConsumer", highlighting the x and y % CIs. We point out the following features seen from Fig. XX: the combination of the two mass paremters is well constrained (a consequence of how a particular combination, the "chirp mass" enters predictions), other parameters also show patterns of dependence, they are however less pronounces. We highlight the non-linear relation between the radius $R_1$ and $\Lambda$ parameter and the two-pronged structure of the radius $R_1$.
For further study we therefore remove m2 from the dataset. We first look at the distribution in a grand tour display, where we use a scatter plot display combined with alpha transperancy to study the density distribution in the 5-d parameter space. The grand tour indicates that the data points are found on a curved surface in the five dimensional space. This may stem from a non-linear relation between the parameters, which we will try to uncover using the above developped formalism for new guided tour index functions.
